\textsf{Are large language models superhuman chemists?}

### 2024-03-22 src/tex/authors.tex
need to think a bit about how to phrase conclusions
parallel coordinates and updated plot
typesetting
affiliations will need reordering

% Question contributors
\credit{Benedict~Emoekabu}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Aswanth~Krishnan}{0,0,0,0,0,0,0,0,1,0,0,0,0,0}
\credit{Tanya~Gupta}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Mara~Wilhemli}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Macjonathan~Oreke}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Tim Hoffmann}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Lea Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jan Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Nicole Roesner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}

% senior authors 
\credit{Michael~Pieler}{1,0,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Philippe~Schwaller}{1,1,0,1,1,0,0,0,0,1,0,0,0,0}
\credit{Kevin Maik Jablonka}{1,1,1,1,1,1,1,1,1,1,1,1,1,1}

\author[1,$\star$]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}
\author[1,$\star$]{Nawaf~Alampara~\orcidlink{}}
\author[1,$\star$]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}
\author[]{Benedict~Emoekabu}
\author[4]{Aswanth~Krishnan~\orcidlink{0009-0008-2703-5613}}
\author[5,6]{Tanya~Gupta}
\author[1]{Mara~Willhelmi}
\author[1]{Macjonathan~Oreke}

\author[7]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[1]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[8]{Amir~Elahi}
\author[]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Tim~Hoffmann}
\author[1]{Lea~Klepsch~\orcidlink{0000-0003-4978-4670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[2, 9]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[1]{Jan~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1]{Nicole~Roesner}

\author[1]{Johanna Schreiber}
\author[1]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[10]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

@@

\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[2]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[3]{Helmholtz Institute for Polymers in Energy Applications Jena (HIPOLE Jena), Philosophenweg 7a, 07743 Jena, Germany}

@@

\affil[8]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Switzerland}
\affil[10]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[11]{OpenBioML.org}
\affil[12]{Stability.AI}
\affil[9]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[4]{QpiVolta Technologies Pvt Ltd}
\affil[7]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, United Kingdom}

\affil[\Letter]{\texttt{mail@kjablonka.com}}
\affil[$\star$]{These authors contributed equally.}

>>>>

% Question contributors
\credit{Benedict~Emoekabu}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Aswanth~Krishnan}{0,0,0,0,0,0,0,0,1,0,0,0,0,0}
\credit{Tanya~Gupta}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Mara~Wilhemli}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Macjonathan~Okereke}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Caroline Holick}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Tim Hoffmann}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Lea~C.~Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jan Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Nicole Roesner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Leanne M. Stafast}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}

% senior authors 
\credit{Michael~Pieler}{1,0,0,1,0,1,0,1,0,0,0,0,0,1}
\credit{Philippe~Schwaller}{1,1,0,1,1,1,0,0,0,1,0,0,0,0}
\credit{Kevin Maik Jablonka}{1,1,1,1,1,1,1,1,1,1,1,1,1,1}

\author[1,$\star$]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}
\author[1,$\star$]{Nawaf~Alampara~\orcidlink{0009-0001-7697-7315}}
\author[1,$\star$]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}
\author[]{Benedict~Emoekabu}
\author[4]{Aswanth~Krishnan~\orcidlink{0009-0008-2703-5613}}
\author[5,6]{Tanya~Gupta}
\author[1]{Mara~Willhelmi}
\author[1]{Macjonathan~Okereke~\orcidlink{0009-0007-1013-0502}}

\author[7]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[13]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[8]{Amir~Elahi}
\author[]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Caroline~Holick}
\author[1]{Tim~Hoffmann}
\author[1]{Lea~C.~Klepsch~\orcidlink{0009-0009-3849-1670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[2, 9]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[1]{Jan~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1]{Nicole~Roesner}

\author[1]{Johanna Schreiber}
\author[1]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[1]{Leanne~M.~Stafast}
\author[10]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

@@

\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[2]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[3]{Helmholtz Institute for Polymers in Energy Applications Jena (HIPOLE Jena), Lessingstrasse 12-14, 07743 Jena, Germany}

@@

\affil[8]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Switzerland}
\affil[10]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[11]{OpenBioML.org}
\affil[12]{Stability.AI}
\affil[9]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[4]{QpiVolta Technologies Pvt Ltd}
\affil[7]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, United Kingdom}
\affil[13]{Macromolecular Chemistry, University of Bayreuth, 95447 Bayreuth, Germany}
\affil[\Letter]{\texttt{mail@kjablonka.com}}
\affil[$\star$]{These authors contributed equally.}
